### 2021-01-06 cleave.tex
start describing experiments

host = 'localhost'
port = 8080

controller_class = 'InvPendulumController'

tick_rate = 100
emu_duration = '30m'

state = InvPendulumState(fail_angle_rad=-1)

@@

actuators = [
    SimpleConstantActuator(initial_value=0, prop_name='force')
]

output_dir = './plant_metrics'
    \end{minted}
    \caption{Example configuration file.}
    \label{lst:config}
\end{listing}

\todo[inline]{Fill in core concepts}
\todo[inline]{Link to repo}

\subsection{General architecture}

The general architecture of CLEAVE centers around two components:

\begin{enumerate}
    \item the Plant, corresponding to the emulated physical system running on some arbitrary client device;
    \item the Controller Service running on some arbitrary cloudlet, which receives samples of the state of the Plant and produces control commands;
\end{enumerate}

These components are connected through the real network

In the following, we will briefly discuss the design and implementation of these components.

\subsubsection{Plant}

As

\subsubsection{Controller Service}
\subsection{Network}

>>>>

host = '0.0.0.0'  # address of dispatch server
port = 8080       # providing Controllers

# Controller parameters
controller_class = 'InvPendulumController'
controller_params = {'ref': 0.0}

# Plant emulation parameters 
tick_rate = 100
emu_duration = '30m'
state = InvPendulumState(fail_angle_rad=0.34)
output_dir = './plant_metrics'

@@

actuators = [
    SimpleConstantActuator(initial_value=0, prop_name='force')
]
    \end{minted}
    \caption{
        Example configuration file.
        Users are simply required to define a number of top-level variables, but are otherwise free to include arbitrary code.
        This allows for the easy extension of emulations.
    }
    \label{lst:config}
\end{listing}

### 2021-01-06 experiments.tex
start describing experiments

>>>>

In this section, we validate the utility of the CLEAVE framework through scalability measurements of a networked control system running on a WiFi link.
With this, we aim to answer questions about the ability of CLEAVE to provide relevant and accurate metrics on the performance of such setups as \emph{system load} increases.
In this context, we will focus on the load as it manifests on the network link in terms of the reliability of the link and the associated latencies. 
We adopt this constrained view of load due to the characteristics of NCS, where controllers are usually relatively lightweight in terms of computing resources, leaving the network link as the principal bottleneck in the system.

Our experimental setup is depicted in \cref{fig:expsetup}.
A number between 1 and 12 of CLEAVE Plants running on dedicated light-weight general purpose computing devices (in this case, Raspberry Pi 4's) connect wirelessly to a WiFi Access Point (AP).
This AP in turn connects via Ethernet to a host on which the CLEAVE Dispatcher and Controllers are executed.

\begin{figure}
    \centering
    \includegraphics[width=3cm]{example-image-a}
    \caption{Experiment setup}
    \label{fig:expsetup}
\end{figure}
